\documentclass[style=elcolors, mode=present]{powerdot}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{epsfig}
\usepackage{anyfontsize}
\usepackage{url}
\pdsetup{
 lf=Security Vulnerability Assessment,
 rf=Assessment Process
}
\title{Vulnerability Assessment Process}
\author{Coleman Kane\\Coleman.Kane@ge.com}
\begin{document}
\maketitle

\begin{slide}{Vulnerability Assessment}
Assessment is the practice of discovering the vulnerabilties posed by an environment, determining their
negative risk impact, and documenting these observations for future planning. In some cases, this may drive
modifications to a network or business practice to eliminate the vulnerability or reduce its exposure. In
other cases, one might implement montioring to notify in the event that an identified vulnerability is being exploited
in the environment.
\end{slide}

\begin{slide}{Methodology: OWASP Approach}
\begin{itemize}
\item Actively developing field
\item As many methodologies as commercial providers
\item OWASP approach describes six steps to develop a risk analysis
\end{itemize}
\end{slide}

\begin{slide}{Basic Heuristic}
Generalized equation:
\begin{itemize}
\item \textbf{Risk = Likelihood * Impact}
\item Identify what exposures you would like to assess the risk of
\item use the process to calculate the Likelihood / Impact of those exposures
\end{itemize}
\end{slide}

\begin{slide}{Step 1: Identify Risk(s)}
Determine what exposure you are concerned about. Some considerations for this:
\begin{itemize}
\item What might a breach objective be?
\item Who might attempt, vs. who would not?
\item What aspects of your business should be in scope / out of scope?
\item What type of attack is in/out of scope?
\item What would your loss cost be?
\end{itemize}

Coming up with realistic and well-defined scenarios/scopes that you are developing to will
ensure the assessment is meaningful for your business cases.
\end{slide}

\begin{slide}{Step 2: Estimating Likelihood}
Two primary contributors to this:
\begin{itemize}
\item Threat Agent factors
\item Vulnerability factors
\end{itemize}

Come up with rating criteria, and a scoring system (for example, 0-9)
\end{slide}

\begin{slide}{Step 2: Likelihood (Threat Agent)}
Better adversaries are expected to have greater success in successfully exposing you. You may grade your adversaries based upon
arbitrarily-selected, applicable criteria.
\begin{itemize}
 \item Skill level: Red teaming skills(9), Network programming skills (7), Scritping skills (4), No skills (1)
 \item Motive: Funding level, priority level - Nation-state (9), Criminal activity (6), Opporutnist (3)
 \item Opportunity: Situational characteristics to increase (9) or decrease (0) the likelihood of attacking
 \item Size: Size of threat agent group, resourcing which can be applied to the attack: Lone actor (1), Small team (3), Army unit (7),
       Internet-scale (9)
\end{itemize}
\end{slide}

\begin{slide}{Step 2: Likelihood (Vulnerability Factors)}
\begin{itemize}
\item Ease of discovery / Security-through-obscurity
\item Ease of exploit
\item Awareness
\item Intrusion detection / instrumentation
\end{itemize}

Many of these items are under direct control of the entity being assessed, and therefore provide the starting measurements
for improvement projects
\end{slide}

\begin{slide}{Step 3: Estimating Impact}
\begin{itemize}
 \item Technical impact, losses of: Confidentiality, integrity, availability, accountability
 \item Business impact: Financial damage, Reputational damage, Non-compliance, Privacy violation
\end{itemize}
\end{slide}

\begin{slide}{Step 4: Determine the Risk Rating}
Use the Impact \& Vulnerability computations earlier to calculate an average value for the purpose
of reporting the risk rating.

Reporting options:
\begin{itemize}
 \item May choose Low/Medium/High/Critical level descriptors
 \item May want to apply weightings to certain criteria
 \item May want to report where recipient is in relation to peers
 \item Frequency of activity/breaches at current risk rating level
\end{itemize}
\end{slide}

\begin{slide}{Step 5: Remediation Planning}
Determine what to fix.

Using the vulnerability ratings, you can scope improvment projects based upon
lower-scoring vulnerability factors.

Options can be reported alongside implementation costs to assist in project selection
and planning.
\end{slide}

\begin{slide}{Step 6: Customizing Risk Rating}
Competing principles:
\begin{itemize}
\item Threat landscape is not a constant, but an ever-changing dynamic system
\item Assessment is most meaningful when it can be kept constant across multiple measurement cycles
\end{itemize}

As time goes on, you'll want to use knowledge of reported activity to inform changes. Possibly overlay "old" and "new" rating
systems in reports, to illustrate ongoing improvement while ensuring that reporitng is kept up to date
\end{slide}

\end{document}
