\documentclass[style=elcolors, mode=present]{powerdot}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{epsfig}
\usepackage{anyfontsize}
\usepackage{url}
\pdsetup{
 lf=Security Vulnerability Assessment,
 rf=Course introduction
}
\title{Security Vulnerability Assessment}
\author{Coleman Kane\\Coleman.Kane@ge.com}
\begin{document}
\maketitle

\begin{slide}{Security Vulnerability}
A security vulnerability is a weakness in a technology or business which can enable an attacker to
gain elevated access, beyond what they are entitled, to secured information. We will primarily scope this
course to vulnerabilities leading to unwanted information or hardware/software system accesses.
\end{slide}

\begin{slide}{Class Scope}
For the purpose of this class, we will be focusing on vulnerabilities in the following areas:
\begin{itemize}
 \item Software bugs \& programming language design which freq. lead to vulnerabilities
 \item Network-based vulnerabilities / attacks
 \item Hardware-based vulnerabilities / attacks
 \item Social-engineering vulnerabilities / attacks
\end{itemize}
\end{slide}

\begin{slide}{Vulnerability Impact}
Vulnerabilities increase the \textbf{defensive risk} to information \& business. Vulnerabilities can be
described in terms of your \textbf{Attack Landscape}, and can be addressed primarily in one of two ways:
\begin{itemize}
 \item Documenting, cataloging, and watching
 \item Changing the landscape
\end{itemize}
\end{slide}

\begin{slide}{Vulnerability Assessment}
Assessment is the practice of discovering the vulnerabilties posed by an environment, determining their
negative risk impact, and documenting these observations for future planning. In some cases, this may drive
modifications to a network or business practice to eliminate the vulnerability or reduce its exposure. In
other cases, one might implement montioring to notify in the event that an identified vulnerability is being exploited
in the environment.
\end{slide}

\begin{slide}{Vulnerability Response}
Typically, a response to a vulnerability will come in one of two forms (per OWASP):
\begin{itemize}
 \item Impact: Should a vulnerability be exploited, reducing the exposure risk and impact
 \item Likelihood: Reducing the probability of leveraging a vulnerability
\end{itemize}
\end{slide}

\begin{slide}{Summary}
This class will discuss a number of common vulnerability causes, the identification and weighting of these, response planning,
responsible disclosure, and how these are commonly leveraged to gain unauthorized access.
\end{slide}

\end{document}
