\documentclass[style=elcolors, mode=present]{powerdot}
\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{epsfig}
\usepackage{anyfontsize}
\usepackage{url}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\pdsetup{
 lf=Security Vulnerability Assessment,
 rf=Malware Propagation
}
\title{Malware Propagation}
\author{Coleman Kane\\Coleman.Kane@ge.com}
\begin{document}
\maketitle

\begin{slide}{Malware Propagation}
Propagation is the term frequently used to describe various distribution methods used by malicious tools. Generally this
is related to the subset of malware which are designed to self-replicate. The common propagation techniques are frequently
implemented in response to common network-level and trust vulnerabilities common in information systems.
\end{slide}

\begin{slide}{Common Techniques}
Some common propagation techinques:
\begin{itemize}
 \item Worm
 \item Virus
 \item Bots / BotNets
 \item Trojan Horses
\end{itemize}
\end{slide}

\begin{slide}{Worms}
Refer to malware tools which propagate via making copies of the entire malicious program or script. 

Common example: Autorun malware
\end{slide}

\begin{slide}{Viruses}
Similar to worms, except rather than transmitting a full copy of the program, a virus is commonly a small amount of shellcode
which is stitched into one or more existing files. This frequently means that a program which was once legitimate will be hijacked
by inserting malicious code alongside exiting code, to make a program that performs both functions.
\end{slide}

\begin{slide}{Bots / BotNets}
One of the more common and public transmission vectors. There are many different types of bots and purposes for these. A common
example is bots which are designed to compromise targets, harvest more targets from contact lists, and subsequently provide the
dual function of being nodes which can be coordinated to email future phishing attacks.
\end{slide}

\begin{slide}{Trojan Horses}
Malware frequently delivered by packaging it inside of a program or file which alleges to perform an entirely different function. These
are frequently used in what are known as "Spearphishing" attacks, as they can be the most difficult and manual types of distribution
methods to construct.
\end{slide}

\end{document}
